Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2018-12-11 paper/snakemajoranas.tex
update paragraph structure (unfinished)

\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
We claim that one of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.
\comment{The gap is small because of long trajectories.}
We claim that this is due to, from a semi classical perspective, long paths through the semiconductor without interruption by the superconductor.
\comment{We show that zigzag geometry solves this problem in a controllable manner.}
We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and avoids the appearance of a soft gap.

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Analytical estimate
%%██████████████████████████████████████████████████████████████████████████
\section{Analytical estimate}
We claim that the hardening of the gap is due to the cutoff of long trajectories.
In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
We then compute the scattering matrix Eq.~\eqref{eq:smatrix} to find the Andreev bound spectrum as a function of the momentum along the strip direction.
We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.

@@

\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian.}

%%██████████████████████████████████████████████████████████████████████████
%%██ Localization lengths and shape effect
%%██████████████████████████████████████████████████████████████████████████
\section{Localization lengths and shape effect}
Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
We then superimpose them onto the geometry, as in figure \ref{fig:wavefunctions}.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
All of the zigzag type geometries however show greatly reduced coherence length.\tabularnewline
This can be explained by two effects: the increase in topological gap, but also the beforementioned reduction of the group velocity.
\comment{We find the Majorana lengths by calculating the slowest decaying mode.}

>>>>

\comment{The gap is small because of long trajectories.}
From a semiclassical perspective, long paths through the semiconductor without interruption by the superconductor.

\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
We claim that one of the problems lying in the way of a stable system, is the appearance of a soft gap; the gap is greatly reduced for states with momentum directed along the length of the strip.

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
We show that introducing a zigzag or snake like geometry for the semiconductor removes these long trajectories and avoids the appearance of a soft gap.

@@

\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian and zigzag geometry.}

%%██████████████████████████████████████████████████████████████████████████
%%██ Analytical estimate
%%██████████████████████████████████████████████████████████████████████████
\section{Analytical estimate of the band gap}

\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}

\comment{We use a short junction approximation and neglect transverse SO.}

\comment{The lowest energy at $|k| < k_\textrm{cutoff}$ sets the band gap.}

We claim that the hardening of the gap is due to the cutoff of long trajectories.
In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
We then compute the scattering matrix Eq.~\eqref{eq:smatrix} to find the Andreev bound spectrum as a function of the momentum along the strip direction.
We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Localization lengths and shape effect
%%██████████████████████████████████████████████████████████████████████████
\section{Localization lengths and shape effect}

\comment{We find the Majorana lengths by calculating the slowest decaying mode.}

\comment{In a zigzag geometry Majoranas are localized within one segment of zigzag.}

\comment{We also confirm that the specific shape does not matter.}

Using the tight-binding package Kwant~\cite{groth_kwant:_2014}, we model a finite system to compute the Majorana wave function density for different geometries; ribbon, zigzag, parallel curve and vertically offset sinusoids.
We then superimpose them onto the geometry, as in figure \ref{fig:wavefunctions}.
For the ribbon system, we see that the Majorana coherence length is relatively large, not showing the decolalized nature sought after.
All of the zigzag type geometries however show greatly reduced coherence length.\tabularnewline
This can be explained by two effects: the increase in topological gap, but also the beforementioned reduction of the group velocity.
